My title

### 2024-11-04 paper/paper.qmd
overview, measurements done

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportstate
#| fig-cap: "Distribution of Support Percentage by State"

@@

# Plotting the support percentages side-by-side for each state
ggplot(plot_data, aes(x = state, y = support_percentage, fill = candidate)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  labs(
    title = "Support Percentages for Harris and Trump by State",
    x = "State",
    y = "Support Percentage"
  ) +
  scale_fill_manual(values = c("Harris" = "blue", "Trump" = "red"), name = "Candidate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

@@

```{r, fig.width= 6, fig.height= 3}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportWP
#| fig-cap:  "Support Percentage for Harris by State since Harris declared as Candidate for Wisconsin and Pennsylvania"
#| label: fig-pollingharris
#| fig-cap: "Polling for Harris By State"

@@

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

Talk way more about it.

@@

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

>>>>

```{r, fig.height= 3}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportstate
#| fig-cap: "Distribution of Support Percentage by State"

@@

# Plotting the support percentages side-by-side for each state
ggplot(plot_data, aes(x = state, y = support_percentage, fill = candidate)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  labs(,
    x = "State",
    y = "Support Percentage"
  ) +
  scale_fill_manual(values = c("Harris" = "blue", "Trump" = "red"), name = "Candidate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1, size = 8))
```

@@

```{r, fig.width= 6, fig.height= 3}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportWP
#| fig-cap:  "Support Percentage for Harris by State since Harris declared as Candidate for Wisconsin and Pennsylvania"

@@

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
Talk more about it.
Talk way more about it.

@@

Add graphs, tables and text.
Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
